Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
boo

The data collected by patients' devices has the potential to create a large volumes of highly structured data. Some sensors
are collecting minute-by-minute data values form multiple sensors 24 hours a day, whereas 
EHRs tend to contain individual records for each clinical session. Therefore, existing methods of storing EHRs may
prove to be unsuitable for the large volumes of data from activity diaries. However, integrating with existing EHRs
would enable clinicians and patients to view the data in context.

To this challenge we present our own personal data platform ``WebBox \cite{webbox}.'' We have used WebBox with EHRs
to enable patient collected data to be augmented with hospital-provided EHR data. WebBox is able to combine
data from multiple sources, and enables patients to make their own annotations against data, and
to optionally share these annotations, along with their activity diaries, with their clinician. This
then enables clinicians and patients to enter into a dialog about how well the patient is doing,
and any lifestyle changes they can make to better their situation.

>>>>

\section{The WebBox EHR Platform}

The high-resolution data collected by activity-sensing devices, accumulated over a long period such as a patient's lifespan, can result in a substantially greater volume of data than current EHR platforms are designed to handle. To this challenge we present our own personal data platform ``WebBox \cite{webbox}.'' We have used WebBox with EHRs
to enable patient collected data to be augmented with hospital-provided EHR data. WebBox is able to combine
data from multiple sources, and enables patients to make their own annotations against data, and
to optionally share these annotations, along with their activity diaries, with their clinician. This
then enables clinicians and patients to enter into a dialog about how well the patient is doing,
and any lifestyle changes they can make to better their situation.

%% Furthermore, Therefore, existing platforms for storing EHRs may
%% prove to be unsuitable for the large volumes of data from activity diaries. However, integrating with existing EHRs
%% would enable clinicians and patients to view the data in context.
